### 2021-04-16 Chapter-6/Chapter-6.tex
Updates from Overleaf

\chapter{Conclusion}\label{chapter6}
This dissertation research studies the address-based side-channel leakages in two aspects: detection and quantification. In the side-channel vulnerability detection research, we explore and solve the two bottlenecks in today's automated side-channel vulnerability detection tool, performance and precision. In the side-channel vulnerability quantification research, we propose two different side-channel leakage quantification tools based on information theory.

@@

\textbf{Compiler-assisted Side-channel Vulnerability Analysis and Mitigation.}
We propose to mitigate the side-channel leakages in a compiler backend. For example, the conditional execution can be eliminated by using the masks. Eliminating side-channel leakages from compilers is not a brand new idea. Coppens et al.~\cite{Coppens:2009:PMT:1607723.1608124} propose several methods to remove several approaches to eliminate all potential leakages that are related to data flow and control flow.  GNU toolchain adds new options (\textsf{-mlfence-after-load}, \textsf{-mlfence-before-indirect-branch}) to mitigate the Load Value Injection (LVI) attack during the compilation. Coppens et al.'s approach has a slowdown with a factor from 2 to 24. The LVI harden binaries generated from GNU toolchains takes 6-10x longer to run. The performance impact from the aggressive mitigation. For example, GNU toolchains inset LFENCE before any possible vulnerable instructions, which include all load instructions, all indirect branches, and return instructions. We plan only to change those points that are more likely to leak sensitive information. Even more, with the tool presented in the dissertation, we can only modify part of the ''severe`` leakage sites.

>>>>

\chapter{Conclusion}\label{chapter6}
This dissertation research studies the address-based side-channel leakages in two aspects: detection and quantification. In the side-channel vulnerability detection research, we explore and solve the two bottlenecks in today's automated side-channel vulnerability detection tool, performance, and precision. In the side-channel vulnerability quantification research, we propose two different side-channel leakage quantification tools based on information theory.

@@

\textbf{Compiler-assisted Side-channel Vulnerability Analysis and Mitigation.}
We propose to mitigate the side-channel leakages in a compiler backend. For example, the conditional execution can be eliminated by using the masks. Eliminating side-channel leakages from compilers is not a brand new idea. Coppens et al.~\cite{Coppens:2009:PMT:1607723.1608124} propose several methods to remove several approaches to eliminate all potential leakages that are related to data flow and control flow.  GNU toolchain adds new options (\textsf{-mlfence-after-load}, \textsf{-mlfence-before-indirect-branch}) to mitigate the Load Value Injection (LVI) attack during the compilation. Coppens et al.'s approach has a slowdown with a factor from 2 to 24. The LVI harden binaries generated from GNU toolchains takes 6-10x longer to run. The performance impact from the aggressive mitigation. For example, GNU toolchains inset LFENCE before any possible vulnerable instructions, which include all load instructions, all indirect branches, and return instructions. We plan only to change those points that are more likely to leak sensitive information. Even more, with the tool presented in the dissertation, we can only modify part of the ``severe'' leakage sites.
